
load("~/Metrics/Lab7/Lab7/NHIS_2014.RData")


```{r}
data_use1$earn_lastyr <- as.factor(data_use1$ERNYR_P)
levels(data_use1$earn_lastyr) <- c("0","$01-$4999","$5000-$9999","$10000-$14999","$15000-$19999","$20000-$24999","$25000-$34999","$35000-$44999","$45000-$54999","$55000-$64999","$65000-$74999","$75000 and over",NA,NA,NA)

```

```{r}
model_logit1 <- glm(NOTCOV ~ AGE_P + I(AGE_P^2) + female + AfAm + Asian + RaceOther  
                    + Hispanic + educ_hs + educ_smcoll + educ_as + educ_bach + educ_adv 
                    + married + widowed + divorc_sep + veteran_stat + REGION + region_born,
                    family = binomial, data = data_use1)
summary(model_logit1)
```

```{r}
d_region <- data.frame(model.matrix(~ data_use1$REGION))
d_region_born <- data.frame(model.matrix(~ factor(data_use1$region_born)))  # snips any with zero in the subgroup
dat_for_analysis_sub <- data.frame(
  data_use1$NOTCOV,
  data_use1$AGE_P,
  data_use1$female,
  data_use1$AfAm,
  data_use1$Asian,
  data_use1$RaceOther,
  data_use1$Hispanic,
  data_use1$educ_hs,
  data_use1$educ_smcoll,
  data_use1$educ_as,
  data_use1$educ_bach,
  data_use1$educ_adv,
  data_use1$married,
  data_use1$widowed,
  data_use1$divorc_sep,
  d_region[,2:4],
  d_region_born[,2:12]) # need [] since model.matrix includes intercept term

names(dat_for_analysis_sub) <- c("NOTCOV",
                                 "Age",
                                 "female",
                                 "AfAm",
                                 "Asian",
                                 "RaceOther",
                                 "Hispanic",
                                 "educ_hs",
                                 "educ_smcoll",
                                 "educ_as",
                                 "educ_bach",
                                 "educ_adv",
                                 "married",
                                 "widowed",
                                 "divorc_sep",
                                 "Region.Midwest",
                                 "Region.South",
                                 "Region.West",
                                 "born.Mex.CentAm.Carib",
                                 "born.S.Am",
                                 "born.Eur",
                                 "born.f.USSR",
                                 "born.Africa",
                                 "born.MidE",
                                 "born.India.subc",
                                 "born.Asia",
                                 "born.SE.Asia",
                                 "born.elsewhere",
                                 "born.unknown")

```

I had to put veteran_stat into the list of sub set, and then also lower down into the standardize funtion that sets the X variables into sobj object.

```{r}
install.packages("standardize")
```

```{r}
require("standardize")
set.seed(654321)
NN <- length(dat_for_analysis_sub$NOTCOV)
# restrict_1 <- as.logical(round(runif(NN,min=0,max=0.6))) # use fraction as training data
restrict_1 <- (runif(NN) < 0.1) # use 10% as training data
summary(restrict_1)
dat_train <- subset(dat_for_analysis_sub, restrict_1)
dat_test <- subset(dat_for_analysis_sub, !restrict_1)
sobj <- standardize(NOTCOV ~ Age + female + AfAm + Asian + RaceOther + Hispanic + 
                      educ_hs + educ_smcoll + educ_as + educ_bach + educ_adv + 
                      married + widowed + divorc_sep + 
                      Region.Midwest + Region.South + Region.West + 
                      born.Mex.CentAm.Carib + born.S.Am + born.Eur + born.f.USSR + 
                      born.Africa + born.MidE + born.India.subc + born.Asia + 
                      born.SE.Asia + born.elsewhere + born.unknown, dat_train, family = binomial)

s_dat_test <- predict(sobj, dat_test)
```

```{r}
summary(sobj$data)
```


```{r}
# LPM
model_lpm1 <- lm(sobj$formula, data = sobj$data)
summary(model_lpm1)
pred_vals_lpm <- predict(model_lpm1, s_dat_test)
pred_model_lpm1 <- (pred_vals_lpm > 0.61)
table(pred = pred_model_lpm1, true = dat_test$NOTCOV)
# logit 
model_logit1 <- glm(sobj$formula, family = binomial, data = sobj$data)
summary(model_logit1)
pred_vals <- predict(model_logit1, s_dat_test, type = "response")
pred_model_logit1 <- (pred_vals > 0.5)
table(pred = pred_model_logit1, true = dat_test$NOTCOV)
```

```{r}
install.packages("randomForest")
```


```{r}
require('randomForest')
set.seed(54321)
model_randFor <- randomForest(as.factor(NOTCOV) ~ ., data = sobj$data, importance=TRUE, proximity=TRUE)
print(model_randFor)
round(importance(model_randFor),2)
varImpPlot(model_randFor)
# look at confusion matrix for this too
pred_model1 <- predict(model_randFor,  s_dat_test)
table(pred = pred_model1, true = dat_test$NOTCOV)
```

```{r}
require(e1071)
# tuned_parameters <- tune.svm(as.factor(NOTCOV) ~ ., data = sobj$data, gamma = 10^(-3:0), cost = 10^(-2:1)) 
# summary(tuned_parameters)
# figure best parameters and input into next
svm.model <- svm(as.factor(NOTCOV) ~ ., data = sobj$data, cost = 10, gamma = 0.1)
svm.pred <- predict(svm.model, s_dat_test)
table(pred = svm.pred, true = dat_test$NOTCOV)
```

```{r}
# Elastic Net
require(glmnet)
model1_elasticnet <-  glmnet(as.matrix(sobj$data[,-1]),sobj$data$NOTCOV) 
# default is alpha = 1, lasso

par(mar=c(4.5,4.5,1,4))
plot(model1_elasticnet)
vnat=coef(model1_elasticnet)
vnat=vnat[-1,ncol(vnat)] # remove the intercept, and get the coefficients at the end of the path
axis(4, at=vnat,line=-.5,label=names(sobj$data[,-1]),las=1,tick=FALSE, cex.axis=0.5) 

plot(model1_elasticnet, xvar = "lambda")
plot(model1_elasticnet, xvar = "dev", label = TRUE)
print(model1_elasticnet)

cvmodel1_elasticnet = cv.glmnet(data.matrix(sobj$data[,-1]),data.matrix(sobj$data$NOTCOV)) 
cvmodel1_elasticnet$lambda.min
log(cvmodel1_elasticnet$lambda.min)
coef(cvmodel1_elasticnet, s = "lambda.min")

pred1_elasnet <- predict(model1_elasticnet, newx = data.matrix(s_dat_test), s = cvmodel1_elasticnet$lambda.min)
pred_model1_elasnet <- (pred1_elasnet < mean(pred1_elasnet)) 
table(pred = pred_model1_elasnet, true = dat_test$NOTCOV)

model2_elasticnet <-  glmnet(as.matrix(sobj$data[,-1]),sobj$data$NOTCOV, alpha = 0) 
# or try different alpha values to see if you can improve
```

Forest and tree model
pred     0     1
   False 87844 11175
   True   604  1247

Support Vector Mechine
pred     0     1
   False 86565 10432
   True  1883  1990

Elastic Net
pred        0     1
  FALSE 60284  4382
  TRUE  28164  8040

The forest model is much better at guessing people who are covered compared to not covered. there are many more incorrect Not covered in this model.

The Support Vector Mechine is better over all then the forest model and is better at determining not covered in comparison to covered.

The Elastic net is the the most accuate model out of the 3 over all. Guessing almost 2/3 of the Covereds correctly and 1/3 of the Not covered correclty. This model is a masive improvement compared to the other two models.

It is interesting to note how the consistancy of the guesses are nott equal between the Covered and Not Covered. So with tweeking to make the models a little more even there could be a way at evening out the accuracy of the guesses between the 0 and 1's by using more then one model.
